---
title: "Re-Naming Sub-epidemic and Spatial-wave forecasts"
author: "Amanda Bleichrodt"
date: "2024-01-28"
output: html_document
---
```{r}
#install.packages("qdapRegex")
library(qdapRegex)
library(stringr)
library(tidyverse)
```

Prior to running this code, please make sure that your working directory is 
set to your Desktop. The n-sub-epidemic and spatial-wave forecasts should be 
located within you desktop, each in separate folders. The n-sub-epidemic folder
should be called "n-sub-epidemic" and the spatial-wave folder should be called
"spatial-wave".

## Preparing for loading the forecasts 

Prior to loading the forecasts from your local system, please enter the names
of the locations or groupings for which you have forecasts. These names 
correspond to the what would have been the column names in the '.txt' file
used in the forecasting process. You must ensure that the order that you list
here matches the order of the columns in your '.txt' file. 

```{r preparing-for-loading}
#############################################
# Order of names or "states" in input files #
#############################################
namesOrder <- c("Brazil", "Canada", "France", "Germany", "Spain", "United-Kingdom", "US-CDC", "US-OWID", "World")

######################
# Calibration period #
######################
calibration.input <- 9
```

After you have set the names, you should not need to make any additional edits
to the code. I will provide descriptions of each step for those who are 
interested in learning more about the code.

# Re-naming the *n*-sub-epidemic forecasts

The forecast file names for the n-sub-epidemic are rather long, and often can
not be opened up due to the length of the file name. This code will re-name
the files, as well as add pertenant information (i.e., locations or groups) to
the file name.

## Calling the specific *n*-sub-epidemic folder 

After setting the working directory, R will know to look within this folder
for the remainder of the code. First (below) it looks for the folder called
"n-sub-epidemic" and calls all of the files saved within the folder. It then 
saves the file pathway names as a "vector" in your global environment.

```{r calling-folder-from-WD}
nSubForecasts <- list.files (path = "n-sub-epidemic/", # Folder with saved forecasts
                             full.names = T) # Telling R we want the full file names 
```

Now that we have a vector of the file names, we then need to loop through each
file, determine the forecast period, and the corresponding "state". The loop 
then creates a new file name, and saves the corresponding forecast under that
file name to a new folder in your working directory.

## Looping through forecasts

Below creates the new folder where the re-named files will be save. The folder
will be created within your working directory (Desktop folder).

### Creating the new folder
```{r creating-the-n-sub-epidemic-folder}
ifelse(!dir.exists("Renamed-NSubEpi"), # Checking to see if the folder exists
       dir.create("Renamed-NSubEpi"), # Creating the folder if it does not exist
       "Folder exists already") # Returning a message if its already creates
```

### Looping through forecasts
```{r forecast-name-loop}

#####################
# Starting the loop #
#####################
for(i in 1:length(nSubForecasts)){
  
  # Calling the forecast file name from the vector above
  forecastName <- nSubForecasts[i]
  
  # Calling the data for the actual forecast
  data <- read.csv(forecastName)
  
  ##########################################
  # Pulling information from the file name #
  ##########################################
  
  # Model name
  model_name <- qdapRegex::ex_between(forecastName, "/", "-onsetfixed")[[1]][1]
  
  # Calibration period
  calibration <- calibration.input
  
  # Determining the time-type for data
  if(grepl("weekly", forecastName)){
    
    timeType <- "weekly"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = anytime::anydate(paste0(year, "-", month, "-", day))) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }else if(grepl("daily", forecastName)){
    
    timeType <- "daily"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = anytime::anydate(paste0(year, "-", month, "-", day))) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }else{
    
    timeType <- "yearly"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = as.numeric(year)) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }
  
  # Weights - Only applicable to ensemble models
  if(grepl("Ensemble", model_name)){
    
    weight <- qdapRegex::ex_between(forecastName, "weighttype-", paste0("-", timeType))[[1]][1]
    
  }else{
    
    weight <- 0
    
  }
  
  # Determining the "area" or group 
  area <- qdapRegex::ex_between(forecastName, "area-", "-")[[1]][1]
  
  # Determining the forecast date
  if(timeType == "yearly"){
    
    forecastDate <- str_sub(forecastName,-8,-5)
    
  }else{
    
    forecastDate <- qdapRegex::ex_between(forecastName, paste0("area-", area, "-"), ".csv")[[1]][1]
    
  }
  
  #######################
  # Creating new labels #
  #######################
  
  # Area name 
  areaName <- namesOrder[as.numeric(area)]
  
  # Weight
  weightName <- switch (weight,
    "-1" = "Unweighted-",
    "1" = "Weighted-",
    NULL
  )
  
  # Forecasting horizon 
  horizon <- qdapRegex::ex_between(forecastName, "horizon-", "-")[[1]][1]
  
  ##############################
  # Creating the new file name #
  ##############################
  newFileName <- paste0("NSE-",
                        paste0(model_name, weightName), 
                        "-horizon-",
                        horizon, 
                        "-calibration-",
                        calibration.input,
                        "-", 
                        areaName,
                        "-",
                        forecastDate,
                        ".csv")
  
  ###############################################
  # Saving the forecast under the new file name #
  ###############################################

  # Saving the forecast under the new name
  write.csv(data, file = paste0("Renamed-NSubEpi/", newFileName), row.names = F)
 
}

```

# Re-naming the spatial-wave forecasts

The forecast file names for the spatial-wave are rather long, and often can
not be opened up due to the length of the file name. This code will re-name
the files, as well as add pertenant information (i.e., locations or groups) to
the file name.

## Calling the specific spatial-wave folder 

After setting the working directory, R will know to look within this folder
for the remainder of the code. First (below) it looks for the folder called
"spatial-wave" and calls all of the files saved within the folder. It then 
saves the file pathway names as a "vector" in your global environment.

```{r calling-folder-from-WD-wave}
WaveForecasts <- list.files (path = "spatial-wave/", # Folder with saved forecasts
                             full.names = T) # Telling R we want the full file names 
```

Now that we have a vector of the file names, we then need to loop through each
file, determine the forecast period, and the corresponding "state". The loop 
then creates a new file name, and saves the corresponding forecast under that
file name to a new folder in your working directory.

## Looping through forecasts

Below creates the new folder where the re-named files will be save. The folder
will be created within your working directory (Desktop folder).

### Creating the new folder
```{r creating-the-wave-folder}
ifelse(!dir.exists("Renamed-SpatialWave"), # Checking to see if the folder exists
       dir.create("Renamed-SpatialWave"), # Creating the folder if it does not exist
       "Folder exists already") # Returning a message if its already creates
```

### Looping through forecasts
```{r forecast-name-loop-wave}
#####################
# Starting the loop #
#####################
for(i in 1:length(WaveForecasts)){
  
  # Calling the forecast file name from the vector above
  forecastName <- WaveForecasts[i]
  
  # Calling the data for the actual forecast
  data <- read.csv(forecastName)
  
  ##########################################
  # Pulling information from the file name #
  ##########################################
  
  # Model name
  model_name <- qdapRegex::ex_between(forecastName, "/", "-onsetfixed")[[1]][1]
  
  # Calibration period
  calibration <- calibration.input
  
  # Determining the time-type for data
  if(grepl("weekly", forecastName)){
    
    timeType <- "weekly"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = anytime::anydate(paste0(year, "-", month, "-", day))) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }else if(grepl("daily", forecastName)){
    
    timeType <- "daily"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = anytime::anydate(paste0(year, "-", month, "-", day))) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }else{
    
    timeType <- "yearly"
    
    # Fixing the dates
    data <- data %>%
      dplyr::mutate(Date = as.numeric(year)) %>%
      dplyr::select(Date, data, median, LB, UB)
    
  }
  
  # Weights - Only applicable to ensemble models
  if(grepl("Ensemble", model_name)){
    
    weight <- qdapRegex::ex_between(forecastName, "weight_type-", paste0("-", timeType))[[1]][1]
    
  }else{
    
    weight <- 0
    
  }
  
  # Determining the "area" or group 
  area <- qdapRegex::ex_between(forecastName, "area-", "-")[[1]][1]
  
  # Determining the forecast date
  if(timeType == "yearly"){
    
    forecastDate <- str_sub(forecastName,-8,-5)
    
  }else{
    
    forecastDate <- qdapRegex::ex_between(forecastName, paste0("area-", area, "-"), ".csv")[[1]][1]
  
  }
  
  #######################
  # Creating new labels #
  #######################
  
  # Area name 
  areaName <- namesOrder[as.numeric(area)]
  
  # Weight
  weightName <- switch (weight,
    "-1" = "(UW)",
    "1" = "(W)",
    NULL
  )
  
  # Forecasting horizon 
  horizon <- qdapRegex::ex_between(forecastName, "horizon-", "-")[[1]][1]
  
  ##############################
  # Creating the new file name #
  ##############################
  newFileName <- paste0("Spatial-",
                        paste0(model_name, weightName), 
                        "-horizon-",
                        horizon, 
                        "-calibration-",
                        calibration.input,
                        "-", 
                        areaName,
                        "-",
                        forecastDate,
                        ".csv")
  
  ###############################################
  # Saving the forecast under the new file name #
  ###############################################
  
  # Saving the forecast under the new name
  write.csv(data, file = paste0("Renamed-SpatialWave/", newFileName), row.names = F)
 
}

```

